\section{Game Rules}
\label{sec:rules}

\begin{enumerate}
  \item The game, called \emph{\gamename}, is played in the arena defined in
        Specification~\ref{spec:arena}. The objective is to collect tokens, and
        to bring them to one's scoring zone in addition to removing opponents
        tokens from your zone.
  \item The arena contains 20 tokens. The layout is detailed in
        Specification~\ref{spec:arena}. Each token of a matching color placed
        in your zone is worth 3 points. Each token of a non-matching color
        placed in your zone is worth -1 points.
  \item At the end of the game, each robot is awarded the sum of the value of
        all tokens within their scoring zone (see rule \ref{rules:token})
  \item An additional 1 bonus point is awarded for any movement from the
        start position of a robot.
  \item \label{rules:token}A token is in a scoring zone if, and only if, it
        has three corners in contact with the floor in the zone.
  \item Participating teams must present their robots to match officials at
        least one minute before the start of each match. They will be asked to
        place their robot in the arena, and vacate the arena at least 30
        seconds before the official start time of the match.
  \item There will be up to 4 robots in each match.
  \item \org may have any number of match officials within the arena, including
        during the course of matches.
  \item At the start of each match, robots must be entirely within their
        starting zones.
  \item At the start of each match, teams will be permitted to lean into the
        arena and start their robots.
  \item Each match lasts $150$ seconds.
  \item Teams cannot touch their robots during the match, but they are
        allowed to restart their robot if it does not move.
  \item At the end of each match, teams must wait for instructions to collect
        their robots or risk disqualification. This is in order to give match
        officials time to record scores.
  \item Teams may be disqualified from one or all matches by match officials,
        for non-compliance with regulations, lateness to the match, or any other
        reason at the discretion of the judge. Teams disqualified before the
        start time of a match will not be permitted to enter a robot.
\end{enumerate}
